%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    %---------------------------------------------------------
    \cventry
    {NLP Engineer} % Job title
    {Medad-AI Co.} % Organization
    {Tehran, Iran} % Location
    {Jul. 2021 - Oct. 2021} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Designed and implemented time-series models to predict sentence boundary in Persian text using LSTM.}
            \item {Created ONNX version for backend API.}
            \item {Prepared and cleaned the Persian Wikipedia dataset for models.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Software Engineer} % Job title
    {Meghyas Co.} % Organization
    {Tehran, Iran} % Location
    {May. 2020 - Aug. 2020} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Led Telegram bot team.}
            \item {Implemented features for showing main shareholders and stock prices based on tsetmc.com.}
            \item {Deployed and maintained products and services to server.}
            \item {Used and designed databases such as MySQL, Redis, and MongoDB (ORM) for storing user and stock data.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Client Side Developer} % Job title
    {Quiz of Kings Co.} % Organization
    {Tehran, Iran} % Location
    {Jul. 2019 - Apr. 2021} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Developed in QuizofKings a word game targeting the Iran market.}
            \item {Redesigned the QuizofKings's client app and migrated from Corona Engine(Lua) to Unity(C\#).}
            \item {Documented new version app and current API's to improve readability of code.}
            \item {Implemented request module which communicates with game client and server.}
        \end{cvitems}
    }

    %---------------------------------------------------------
\end{cventries}